What do incoming university students believe about open science practices in

### 2021-04-01 analysis/Manuscript.Rmd
remove extra corr code

# I'm sure there's a way to automate it, but I can't figure it out...just hard code it
# all_cnorms <- df %>% 
#     select(ends_with("_cnorm"))
#   
# corr <- round(cor(all_), ends_with("_cnorm"),2)))
# 
# 
#   all_norms %>% 
#     cor(ends_with("_norm"), ends_with("_cnorm"))
#   
#  
#   cor(all_norms, method = "pearson") %>% 
#   as.tibble()
# 
# all_correlation <- df %>% 
#     select(c(ends_with("_norm"), ends_with("_cnorm"))) %>% 
#   mutate(item = row.names(.)) %>% 
#   select(item, everything())

# this code works, but I must be able to do this all at once...

# breadcrumbs: when I come back to this, I need to combine these in a tibble
  # and then join it with the existing table...I probably need to mutate, but I 
  # need to sort out how to do this...

# practice_corr <- practice_means %>% 
  # mutate()

critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)

info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)

open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)

open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)

open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)

phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)

preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)

prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)

rbind()

>>>>

# just keeping this here for now, but will be able to delete
# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
# 
# hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
# hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
# 
# info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
# info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
# 
# open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
# open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
# 
# open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
# open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
# 
# open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
# open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
# 
# phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
# phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
# 
# preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
# preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
# 
# prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
# prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)
